\papertitle

### 2014-03-20 final-report/paper.tex
Figure instead of Fig.

The \fragment view comprises two charts: the utilization chart and the
operators chart. The utilization chart (Fig.~\ref{fig:utilization_chart}) shows on
how many workers a fragment is running over time. The chart is used to
quickly reveal any patterns in the schedule, like tail latency, long periods of
idleness, etc. We implemented a small brush (at the top of the figure) that
allows the user to zoom-in and further analyze the problematic area.

@@

The utilization chart also implements a brush that allows the user to further
analyze the query execution by displaying the schedule of each of the worker
nodes, in the operators chart (Fig.~\ref{fig:operators_chart}). The per-worker
schedule shows what operators the worker executed and for how long.

@@

The Worker Communication view consists of two charts: the aggregate communication 
chart and the time series chart. The aggregate communication chart is a matrix representing
a cluster of $N$ workers. Each cell $m,n$ in the matrix represents the total number of tuples sent
by worker $m$ to worker $n$ during the query execution. Figure \ref{fig:matrix} shows this chart along 
with the selected link in the query plan DAG. Hovering the mouse over a cell brings up a tooltip
stating the total number of tuples exchanged between the source and destination workers. The intensity
of the cell color reflects the number of tuples exchanged, i.e., a larger number translates into a darker color 
and a smaller number results in a lighter color. The color pallet used is grayscale and hence
immune to color-blindness issues. The color scale uses LAB interpolation.
The matrix chart representing aggregate communication 
between workers help uncover data skew issues, as discussed in \S \ref{sec:eval}.

@@

When the user clicks on a matrix cell, they are able to view the breakdown of the worker pair communication in a 
time series chart below the matrix. The user can select multiple such cells to compare different time 
series. Figure \ref{fig:ts} shows an example when the user selected two pairs: (8-2) and (7-6). The x-axis shows
time in seconds and y-axis shows number of tuples exchanged between the source and destination workers.
Just looking at the matrix chart it is evident that there is more data exchanged between the source-destination pair
(8-2) than the pair (7-6). But as the time series comparison shows, there is more communication between (7-6)
than (8-2) for the last 2.5 seconds of the query execution. This points to interesting patterns as to the rate at which 
work is done at different workers at different stages of the execution. Distinct points on the lines are highlighted as
black dots. Hovering the cursor over a dot shows the information for that data point in a tooltip. Meanwhile the cells 
in the matrix remain highlighted with the same color used to draw the corresponding time series line. This aids in the
user keeping track of the mapping between the matrix cell and the corresponding time series line. We also provide 
a 'clear selection' button that erases everything from the time series chart upon clicking. Finally we provide the
functionality whereby clicking a row or column label selects every cell in that row or column and displays the 
corresponding time series in the time series chart.

>>>>

The \fragment view comprises two charts: the utilization chart and the
operators chart. The utilization chart (Figure~\ref{fig:utilization_chart}) shows on
how many workers a fragment is running over time. The chart is used to
quickly reveal any patterns in the schedule, like tail latency, long periods of
idleness, etc. We implemented a small brush (at the top of the figure) that
allows the user to zoom-in and further analyze the problematic area.

@@

The utilization chart also implements a brush that allows the user to further
analyze the query execution by displaying the schedule of each of the worker
nodes, in the operators chart (Figure~\ref{fig:operators_chart}). The per-worker
schedule shows what operators the worker executed and for how long.

@@

The Worker Communication view consists of two charts: the aggregate communication 
chart and the time series chart. The aggregate communication chart is a matrix representing
a cluster of $N$ workers. Each cell $m,n$ in the matrix represents the total number of tuples sent
by worker $m$ to worker $n$ during the query execution. Figure~\ref{fig:matrix} shows this chart along 
with the selected link in the query plan DAG. Hovering the mouse over a cell brings up a tooltip
stating the total number of tuples exchanged between the source and destination workers. The intensity
of the cell color reflects the number of tuples exchanged, i.e., a larger number translates into a darker color 
and a smaller number results in a lighter color. The color pallet used is grayscale and hence
immune to color-blindness issues. The color scale uses LAB interpolation.
The matrix chart representing aggregate communication 
between workers help uncover data skew issues, as discussed in \S \ref{sec:eval}.

@@

When the user clicks on a matrix cell, they are able to view the breakdown of the worker pair communication in a 
time series chart below the matrix. The user can select multiple such cells to compare different time 
series. Figure~\ref{fig:ts} shows an example when the user selected two pairs: (8-2) and (7-6). The x-axis shows
time in seconds and y-axis shows number of tuples exchanged between the source and destination workers.
Just looking at the matrix chart it is evident that there is more data exchanged between the source-destination pair
(8-2) than the pair (7-6). But as the time series comparison shows, there is more communication between (7-6)
than (8-2) for the last 2.5 seconds of the query execution. This points to interesting patterns as to the rate at which 
work is done at different workers at different stages of the execution. Distinct points on the lines are highlighted as
black dots. Hovering the cursor over a dot shows the information for that data point in a tooltip. Meanwhile the cells 
in the matrix remain highlighted with the same color used to draw the corresponding time series line. This aids in the
user keeping track of the mapping between the matrix cell and the corresponding time series line. We also provide 
a 'clear selection' button that erases everything from the time series chart upon clicking. Finally we provide the
functionality whereby clicking a row or column label selects every cell in that row or column and displays the 
corresponding time series in the time series chart.
